---
title: "R Final Project_H1B"
output: word_document
---
Loading Packages & Datasets
```{r}
library(stringr)
library(dplyr)
library(lubridate)
library(ggplot2)
library(rvest)
library(ggmap)
library(tidyr)
library(tm)
library(wordcloud)
library(gridExtra)
library(twitteR)

masterdata = read.csv("h1b_kaggle.csv")
year2017 = read.csv("H-1B_FY2017.csv")
year2018= read.csv("H-1B_FY2018.csv")
```

Data Consolidation - merge data from year 2011 to 2018
```{r}
year2017 = year2017[,2:53]

colnames(year2017) == colnames(year2018)
colnames(year2018)[1] = "CASE_NUMBER"
colnames(year2018)[43] = "H1B_DEPENDENT"

year2017$YEAR = 2017
year2018$YEAR = 2018

year2018$PREVAILING_WAGE = str_replace_all(year2018$PREVAILING_WAGE,",","")

twoyears = rbind(year2017,year2018)

twoyears = select(twoyears, "CASE_NUMBER", "CASE_STATUS", "EMPLOYER_NAME", "JOB_TITLE", "SOC_NAME",
                  "FULL_TIME_POSITION", "PREVAILING_WAGE", "PW_UNIT_OF_PAY", "WORKSITE_CITY", "WORKSITE_STATE","YEAR")

levels(twoyears$PW_UNIT_OF_PAY)

twoyears$PREVAILING_WAGE = as.numeric(as.character(twoyears$PREVAILING_WAGE))

twoyears$PREVAILING_WAGE = ifelse(twoyears$PW_UNIT_OF_PAY == "Bi-Weekly",
                                  twoyears$PREVAILING_WAGE * 26,
                                  ifelse(twoyears$PW_UNIT_OF_PAY == "Hour",
                                          twoyears$PREVAILING_WAGE *2080,
                                          ifelse(twoyears$PW_UNIT_OF_PAY == "Month",
                                                 twoyears$PREVAILING_WAGE * 12,
                                                 ifelse(twoyears$PW_UNIT_OF_PAY == "Week",
                                                        twoyears$PREVAILING_WAGE * 52,
                                                        twoyears$PREVAILING_WAGE))))


stateslink = "https://www.50states.com/abbreviations.htm"
statestable = stateslink %>%
  read_html() %>%
  html_nodes(xpath = '//*[@id="content"]/div[1]/table') %>%
  html_table()

statestable = statestable[[1]]
statestable = statestable[c(1:50,52:60),]
colnames(statestable) = c("full_name","Abbreviation")

twoyears_states = full_join(twoyears,statestable, by = c("WORKSITE_STATE" = "Abbreviation"))

masterdata = masterdata %>%
  separate(col = WORKSITE, into = c("WORKSITE_CITY", "WORKSITE_STATE"), sep = ", ")

masterdata = masterdata[,c(1:8,10)]
twoyears_states = twoyears_states[,c(1:3,5,4,6:7,11:12)]

colnames(masterdata) = c("CASE_NUMBER", "CASE_STATUS", "EMPLOYER_NAME", "SOC_NAME","JOB_TITLE",
                         "FULL_TIME_POSITION", "PREVAILING_WAGE", "YEAR", "WORKSITE_STATE")

colnames(twoyears_states) = c("CASE_NUMBER", "CASE_STATUS", "EMPLOYER_NAME", "SOC_NAME","JOB_TITLE",
                         "FULL_TIME_POSITION", "PREVAILING_WAGE", "YEAR", "WORKSITE_STATE")

colnames(masterdata)==colnames(twoyears_states)

final = rbind(masterdata,twoyears_states)
```


Data Cleansing,Standardize Data Format, And Output Master Dataset
```{r}
final = final %>%
  filter(CASE_STATUS != "NA",
         FULL_TIME_POSITION != "",
         PREVAILING_WAGE != "NA",
         WORKSITE_STATE != "NA",
         SOC_NAME != "NA")

final$CASE_NUMBER = seq.int(nrow(final))

final$CASE_STATUS = as.factor(tolower(final$CASE_STATUS))
final$EMPLOYER_NAME = as.factor(tolower(final$EMPLOYER_NAME))
final$SOC_NAME = as.factor(tolower(final$SOC_NAME))
final$JOB_TITLE = as.factor(tolower(final$JOB_TITLE))
final$FULL_TIME_POSITION = as.factor(tolower(final$FULL_TIME_POSITION))
final$WORKSITE_STATE = as.factor(tolower(final$WORKSITE_STATE))
final$YEAR = as.integer(final$YEAR)

write.csv(final,"master.csv")
```

Overall Situation of H1B Application From 2011 to 2018
```{r}
Total_Applicant = final %>%
  group_by(YEAR,CASE_STATUS) %>%
  summarize(count = n()) %>%
  filter(YEAR != "NA") %>%
  spread(key = CASE_STATUS,value = count)

Total_Applicant = Total_Applicant[,-c(5,6,7)]

Total_Applicant = Total_Applicant %>%
  mutate(TTL = sum(certified+`certified-withdrawn`+denied+withdrawn))

Total_Applicant$Applicant = ifelse(Total_Applicant$TTL>600000,"High","Low")

ggplot(Total_Applicant,aes(x = YEAR, y = TTL,fill = Applicant))+
  geom_col()+
  coord_flip()+
  ggtitle("The Total Application Received By LCA From 2011 To 2018") +
  ylab("") +
  xlab("")+
  scale_x_continuous(breaks = seq(2011,2018,1),labels = seq(2011,2018,1))+
  scale_y_continuous(breaks = seq(0,600000,200000),labels = c("0","200,000","400,000","600,000"))+
  scale_fill_manual(values = c("darkred","lightblue"))
```
```{r}
Percent_Certified = Total_Applicant %>%
  summarize(Percent = certified/TTL*100)

ggplot(Percent_Certified,aes(x= YEAR, y = Percent))+
  geom_line()+
  geom_point(aes(x = YEAR, y = Percent),color ="red")+
  ylab("")+
  xlab("")+
  ggtitle("The Pecentage of CERTIFIED From 2011 To 2018")+
  scale_y_continuous(breaks = seq(84,90,1),labels = c("84%","85%","86%","87%","88%","89%","90%"))+
  scale_x_continuous(breaks = seq(2011,2018,1),labels =seq(2011,2018,1))
```
```{r}
final$Certified = ifelse(final$CASE_STATUS == "certified","Certified","Non-certified")

K = final %>%
  group_by(YEAR,Certified) %>%
  summarize(count =n())

ggplot(K,aes(x = YEAR, y= count,fill = Certified)) +
  geom_col()+
  ggtitle("The Percantage of CERTIFIED From 2011 To 2018")+
  xlab("")+
  ylab("")+
  scale_x_continuous(breaks = seq(2011,2018,1),labels = seq(2011,2018,1))+
  scale_y_continuous(breaks = seq(0,600000,200000),labels = c("0","200,000","400,000","600,000"))

```


```{r}
top10job=final%>%
  group_by(JOB_TITLE)%>%
  mutate(Count=n())%>%
  arrange(desc(Count))%>%
  distinct(JOB_TITLE,.keep_all = TRUE)

top10job=top10job[1:10,]
top10job$JOB_TITLE=as.factor(top10job$JOB_TITLE)

ggplot(top10job,aes(reorder(JOB_TITLE,Count),
                    y=Count,
                    fill=Count))+
  geom_col()+
  coord_flip()+
  scale_y_continuous(breaks=seq(0,400000,50000))+
  xlab("Job Title")+
  ylab(NULL)+
  scale_fill_gradient(low="orange",
                      high="dark red",
                      guide=FALSE)+
  ggtitle("Top 10 Jobs for H1B")+
  theme(plot.title = element_text(hjust  =0.5))+
  xlab("")
```


```{r}
top10company=final%>%
  group_by(EMPLOYER_NAME)%>%
  mutate(Count=n())%>%
  arrange(desc(Count))%>%
  distinct(EMPLOYER_NAME,.keep_all = TRUE)
top10company$EMPLOYER_NAME=toupper(top10company$EMPLOYER_NAME)
  

top10company=top10company[1:10,]

ggplot(top10company,aes(reorder(EMPLOYER_NAME,Count),
                        y=Count,
                        fill=Count))+
  geom_col()+
  coord_flip()+
  scale_y_continuous(breaks=seq(0,400000,50000))+
  xlab("Company Name")+
  ylab(NULL)+
  scale_fill_gradient(low="light blue",
                      high="dark blue",
                      guide=FALSE)+
  ggtitle("Top 10 Companies for H1B")+
  xlab("")+
  theme(plot.title = element_text(hjust  =0.5))
```

Distribution of Different Statuses Across US
```{r}
M = final %>%
  select(CASE_STATUS,WORKSITE_STATE)%>%
  group_by(CASE_STATUS,WORKSITE_STATE) %>%
  summarize(count =n())%>%
  spread(key = CASE_STATUS,value  =count)

M = M[,-c(5,6,7)]
M = M[-c(9,28,41),]

state_map = map_data("state")
state_map = state_map[,-6]

N  = full_join(state_map,M,by = c("region"="WORKSITE_STATE"))

p1 = ggplot(N, aes(x =long, 
                   y= lat,
                   group = group,       
                   fill= certified))+
  geom_polygon( color = "black")+
  theme_void()+
  scale_fill_gradient(low = "white",high = "darkred") +
  coord_map("polyconic")+
  ggtitle("CERTIFIED")+
  theme(legend.title = element_blank())

p2 = ggplot(N, aes(x =long, 
                   y= lat,
                   group = group,       
                   fill= certified-withdrawn))+
  geom_polygon( color = "black")+
  theme_void()+
  scale_fill_gradient(low = "white",high = "darkred") +
  coord_map("polyconic")+
  ggtitle("CERTIFIED-WITHDRAWN")+
  theme(legend.title = element_blank())

p3  = ggplot(N, aes(x =long, 
                    y= lat,
                    group = group,       
                    fill= denied))+
  geom_polygon( color = "black")+
  theme_void()+
  scale_fill_gradient(low = "white",high = "darkred") +
  coord_map("polyconic")+
  ggtitle("DENIED")+
  theme(legend.title = element_blank())

p4 = ggplot(N, aes(x =long, 
                   y= lat,
                   group = group,       
                   fill= withdrawn))+
  geom_polygon( color = "black")+
  theme_void()+
  scale_fill_gradient(low = "white",high = "darkred") +
  coord_map("polyconic")+
  ggtitle("WITHDRAWN")+
  theme(legend.title = element_blank())


grid.arrange(p1,p2,p3,p4,nrow=2,ncol=2)
```

Living Cost Index And Salary Index
```{r}
page = "https://www.missourieconomy.org/indicators/cost_of_living/"

Index = page %>%
  read_html() %>%
  html_nodes(xpath = '/html/body/div[5]/div/table') %>%   
  html_table()
Index = Index[[1]]
Index = Index[-1,]
colnames(Index) = c("State","Rank","Index","Grocery","Housing","Utlities","Transportation","Health","Misc.")
Index = Index[-1,]

Index$Index = as.numeric(Index$Index)

Top10_livingcost_index = Index %>%
  arrange(-Index) %>%
  slice(1:10)

ggplot(Top10_livingcost_index,aes(x = reorder(State,Index),
                                  y = Index,
                                  fill = State,
                                  color = State,
                                  label = Index))+
  coord_flip()+
  geom_col()+
  geom_text(nudge_y = 5)+
  ggtitle("Top10 States of Living Cost Index")+
  xlab("")+
  ylab("")+
  theme(legend.position="none")+
  theme(plot.title = element_text(hjust  =0.5))
```
```{r}
salary = final %>%
  select(PREVAILING_WAGE,WORKSITE_STATE)

avg_state = salary %>%
  filter(! is.na(PREVAILING_WAGE)) %>%
  group_by(WORKSITE_STATE) %>%
  summarize(avg_state = mean(PREVAILING_WAGE))

avg_overall = salary %>%
  filter(! is.na(PREVAILING_WAGE)) %>%
  summarize(avg = mean(PREVAILING_WAGE))

avg_state$avg_overall = c(rep(146998.4,57))
avg_state$salary_index = avg_state$avg_state/avg_state$avg_overall*100
avg_state$salary_index = round(avg_state$salary_index,1)

top10_salaery_index = avg_state%>%
  arrange(-salary_index) %>%
  slice(1:10)

ggplot(top10_salaery_index,aes( x = reorder(WORKSITE_STATE,salary_index),
                                y = salary_index,
                                fill = WORKSITE_STATE,
                                color = WORKSITE_STATE,
                                label = salary_index))+
  geom_col()+
  coord_flip()+
  geom_text(nudge_y = 5)+
  xlab("") +
  ylab("") +
  ggtitle("Top10 States of Salary Index")+
  theme(legend.position = "none ") +
  theme(plot.title = element_text(hjust  =0.5))
```

Distributions of Two Indexes Across U.S.
```{r}
Index$State = tolower(Index$State)
Index = Index[,-2]
Index = Index[,-c(3:8)]

LC_map = full_join(Index,state_map, by= c("State" = "region"))

str(LC_map)
LC_map$Index = as.numeric(LC_map$Index)

LCindex = ggplot(LC_map, aes(x =long, 
                             y= lat,
                             group = group,       
                             fill= Index))+
  geom_polygon(color = "black")+
  theme_void()+
  scale_fill_gradient(low = "white",high = "darkred") +
  coord_map("polyconic")+
  theme(legend.title = element_blank())+
  ggtitle("Living Cost by States")+
  theme(plot.title = element_text(hjust = 0.5))

S_map = full_join(Index,state_map, by = c("State" = "region"))

str(S_map)
S_map$Index = as.numeric(S_map$Index)

sindex = ggplot(S_map, aes(x =long, 
                           y= lat,
                           group = group,       
                           fill= Index))+
  geom_polygon(color = "black")+
  theme_void()+
  scale_fill_gradient(low = "white",high = "darkred") +
  coord_map("polyconic")+
  theme(legend.title = element_blank())+
  ggtitle("Salary Index by States")+
  theme(plot.title = element_text(hjust = 0.5))

grid.arrange(LCindex,sindex,nrow=1,ncol=2)
```


```{r}
avg_state$WORKSITE_STATE = as.character(avg_state$WORKSITE_STATE)


combine_two_index = full_join(avg_state,Index, by = c("WORKSITE_STATE" = "State"))

combine_two_index = combine_two_index %>%
  filter(!is.na(Index) & !is.na(salary_index)) %>%
  arrange(Index)

combine_two_index$Index = as.numeric(combine_two_index$Index)
combine_two_index$salary_index = as.numeric(combine_two_index$salary_index)
combine_two_index$diff = ifelse(combine_two_index$salary_index>combine_two_index$Index,"Good","Bad" )

ggplot(combine_two_index,aes(x = salary_index,
                             y = Index,
                             color = diff))+
  geom_point()+
  geom_text(aes(label = WORKSITE_STATE),hjust = 1.2,vjust = 0.8)+
  geom_abline(slope = 1)+
  xlab("Salary Index")+
  ylab("Living Cost Index")+
  scale_x_continuous(breaks = seq(40,200,20))+
  scale_y_continuous(breaks = seq(80,180,20))+
  ggtitle("More Desireable Place For A Job")+
  theme(plot.title = element_text(hjust  =0.5))
```


Salary Trend From 2011 to 2018
```{r}
 final %>%
  filter(YEAR,PREVAILING_WAGE) %>%
  group_by(YEAR) %>%
  summarize(avg = mean(PREVAILING_WAGE,rm.na  =T)) %>%
   ggplot(aes(x = YEAR,
              y = avg))+
   geom_line()+
   geom_point(size =3, color = "red")+
   scale_x_continuous(breaks = seq(2011,2018,1))+
   ggtitle("Average Salary Trend From 2011 To 2018")+
   theme(plot.title = element_text(hjust  =0.5))+
   scale_y_continuous(breaks = seq(90000,180000,30000),labels = c("90,000","120,000","150,000","180,000"))+
   ylab("")+
   xlab("")
```

Distrubition of Salary From 2011 to 2018
```{r}
Density2018 = final %>%
  filter(CASE_STATUS == "certified" & YEAR == "2018")
Density2018$YEAR = as.factor(Density2018$YEAR)

Density2017 = final %>%
  filter(CASE_STATUS == "certified" & YEAR == "2017")
Density2017$YEAR = as.factor(Density2017$YEAR)

Density2016 = final %>%
  filter(CASE_STATUS == "certified" & YEAR == "2016")
Density2016$YEAR = as.factor(Density2016$YEAR)

Density2015 = final %>%
  filter(CASE_STATUS == "certified" & YEAR == "2015")
Density2015$YEAR = as.factor(Density2015$YEAR)

Density2014 = final %>%
  filter(CASE_STATUS == "certified" & YEAR == "2014")
Density2014$YEAR = as.factor(Density2014$YEAR)

Density2013 = final %>%
  filter(CASE_STATUS == "certified" & YEAR == "2013")
Density2013$YEAR = as.factor(Density2013$YEAR)

Density2012 = final %>%
  filter(CASE_STATUS == "certified" & YEAR == "2012")
Density2012$YEAR = as.factor(Density2012$YEAR)

Density2011 = final %>%
  filter(CASE_STATUS == "certified" & YEAR == "2011")
Density2011$YEAR = as.factor(Density2011$YEAR)


ggplot(Density2018, aes(x = PREVAILING_WAGE,fill = YEAR)) + 
  geom_density(alpha = 0.9, position = "identity")+
  geom_density(data = Density2017,
               aes(x = PREVAILING_WAGE,fill = YEAR),
               alpha = 0.7,color = NA,position = "identity")+
  geom_density(data = Density2016,
               aes(x = PREVAILING_WAGE,fill = YEAR),
               alpha = 0.6,color = NA,position = "identity")+
  geom_density(data = Density2015,
               aes(x = PREVAILING_WAGE,fill = YEAR),
               alpha = 0.1,color = NA,position = "identity")+
  geom_density(data = Density2014,
               aes(x = PREVAILING_WAGE,fill = YEAR),
               alpha = 0.1,color = NA,position = "identity")+
  geom_density(data = Density2013,
               aes(x = PREVAILING_WAGE,fill = YEAR),
               alpha = 0.1,color = NA,position = "identity")+
  geom_density(data = Density2012,
               aes(x = PREVAILING_WAGE,fill = YEAR),
               alpha = 0.1,color = NA,position = "identity")+
  geom_density(data = Density2011,
               aes(x = PREVAILING_WAGE,fill = YEAR),
               alpha = 0.1,color = NA,position = "identity")+
  theme(legend.title = element_blank())+
  theme(plot.title = element_text(hjust = 0.5))+
  ggtitle("Salary Distribution From 2011 to 2018")+
  xlab("Salary Level")+
  xlim(8000,150000)
```


```{r}
tech = final %>%
  filter(EMPLOYER_NAME !="NA")

tech$SOC_NAME = as.character(tech$SOC_NAME)
testtech = ifelse(str_detect(tech$SOC_NAME,c("computer","software"))==TRUE,print(tech$CASE_NUMBER),"")
com = tech %>%
  filter(CASE_NUMBER == testtech)
unique(com$SOC_NAME)


testtech1 = ifelse(str_detect(tech$SOC_NAME,"engineer")==TRUE,print(tech$CASE_NUMBER),"")
eng = tech %>%
      filter(CASE_NUMBER == testtech1)

testtech2 = ifelse(str_detect(tech$SOC_NAME,"science")==TRUE,print(tech$CASE_NUMBER),"")
sci = tech %>%
  filter(CASE_NUMBER == testtech2)

testtech3 = ifelse(str_detect(tech$SOC_NAME,"math")==TRUE,print(tech$CASE_NUMBER),"")
math = tech %>%
  filter(CASE_NUMBER == testtech3)

Tec =rbind(com,eng,sci,math)

Tec = Tec %>%
  group_by(CASE_NUMBER)
Tec=Tec[!duplicated(Tec$CASE_NUMBER),]

Tec$Tech = "YES"
Tec$Tech =as.factor(Tec$Tech)


ggplot(Tec,aes(x = PREVAILING_WAGE,fill = Tech))+
  geom_density(alpha = 0.5,color =NA, position = "identity")+
  xlim(10000,400000)

techcase = Tec$CASE_NUMBER

Nontech=final%>%
  filter(!CASE_NUMBER %in% techcase)
Nontech$tech="NO"
Nontech$tech=as.factor(Nontech$tech)


ggplot(Tec,aes(x = PREVAILING_WAGE,fill = Tech))+
  geom_density(alpha = 0.5,color =NA, position = "identity")+
  geom_density(data = Nontech,aes(x = PREVAILING_WAGE, fill = tech),
               alpha = 0.5,color =NA, position = "identity")+
  xlim(10000,200000)+
  ggtitle("The Salary Distribution of Tech and Non-Tech")


Teccr= filter(Tec,CASE_STATUS =="certified")
tecrate = round(nrow(Teccr)/(nrow(Tec))*100,2)


Nontechcr = filter(Nontech,CASE_STATUS == "certified")
Nontechrate= round(nrow(Nontechcr)/(nrow(Nontech))*100,2)
```


The Salary Distribution of Education Industry 
```{r}
edu = final %>%
  filter(CASE_STATUS == "certified") %>%
  filter(EMPLOYER_NAME !="NA")

## Find University
edu$EMPLOYER_NAME = as.character(edu$EMPLOYER_NAME)

test = ifelse(str_detect(edu$EMPLOYER_NAME,"univeristy")==TRUE,print(edu$CASE_NUMBER),"")
unique(test)
Uni = edu %>%
  filter(CASE_NUMBER == test)


test1 = ifelse(str_detect(edu$EMPLOYER_NAME,"school")==TRUE,print(edu$CASE_NUMBER),"")
unique(test1)
Sch = edu %>%
  filter(CASE_NUMBER == test1)


test2 = ifelse(str_detect(edu$EMPLOYER_NAME,"college")==TRUE,print(edu$CASE_NUMBER),"")
unique(test2)
Col = edu %>%
  filter(CASE_NUMBER == test2)


Edu =rbind(Uni,Sch,Col)
EDU = Edu %>%
  group_by(CASE_NUMBER)
EDU$Education = rep("Education",40748)
EDU$Education =as.factor(EDU$Education)


ggplot(EDU,aes(x = PREVAILING_WAGE,fill = Education))+
  geom_density(alpha = 0.5,color =NA, position = "identity")+
  xlim(10000,400000)+
  theme(plot.title = element_text(hjust  =0.5))+
  xlab("")+
  ylab("")+
  ggtitle(" Salary Distribution of Education")
```

Compare The Salary Distribution of Education With Non-Education
```{r}

test4 = ifelse(str_detect(final$EMPLOYER_NAME,c("college","university","school")) == FALSE,print(edu$CASE_NUMBER),"")

unique(test4)

cdata = final %>%
  filter(CASE_STATUS == "certified")

Non_EDU = cdata %>%
  filter(CASE_NUMBER %in% test4)

Non_EDU$Education = rep("Non_Education",3447722)
  

ggplot(EDU,aes(x = PREVAILING_WAGE,fill = Education))+
  geom_density(alpha = 0.5,color =NA, position = "identity")+
  geom_density(data = Non_EDU,aes(x = PREVAILING_WAGE, fill = Education),
               alpha = 0.5,color =NA, position = "identity")+
  xlim(10000,200000)+
  ggtitle("The Salary Distribution of Education and Non-Education")+
  xlab("")+
  ylab("")+
  theme(plot.title = element_text(hjust  =0.5))
```

The Certified Rate of Education & Non-education
```{r}
educr = final %>%
  filter(EMPLOYER_NAME !="NA")


educr$EMPLOYER_NAME = as.character(educr$EMPLOYER_NAME)

test = ifelse(str_detect(educr$EMPLOYER_NAME,"univeristy")==TRUE,print(educr$CASE_NUMBER),"")
Uni = educr %>%
  filter(CASE_NUMBER == test)


test1 = ifelse(str_detect(educr$EMPLOYER_NAME,"school")==TRUE,print(educr$CASE_NUMBER),"")
Sch = educr %>%
  filter(CASE_NUMBER == test1)


test2 = ifelse(str_detect(educr$EMPLOYER_NAME,"college")==TRUE,print(educr$CASE_NUMBER),"")
Col = educr %>%
  filter(CASE_NUMBER == test2)

Educr =rbind(Uni,Sch,Col)

Edu_CR =round(nrow(EDU)/nrow(Educr)*100,2)

Non_Edu_CR = round(nrow(Non_EDU)/(nrow(final)-nrow(Educr))*100,2)
```

Twitter & Word Cloud
```{r}
api_key = "ygI5ryuik1SQu0dLISlfmYsiF"
api_secret = "kIQH3FhtLi5fQy6jrFS7XISWQjVWRw9WG78tflZoLqWhRarleP"
access_token = "980611835387772928-ituutfwksxFdet6KagqJebehcABIWAu"
access_token_secret = "RKkkqFs9hpfLoP4iP6pSWhdBpPSz6ju3wsDqpiHHgX71q"

setup_twitter_oauth(api_key, api_secret, access_token, access_token_secret)


TweetsH1B = searchTwitter(searchString = "H1B",n = 200)
H1BDF = twListToDF(TweetsH1B)

nohandles = str_replace_all(H1BDF$text,
                            pattern = "@\\w+",
                            replacement = "")

wordCorpus = Corpus(VectorSource(nohandles)) %>%
  tm_map(removePunctuation) %>%
  tm_map(content_transformer(tolower)) %>%
  tm_map(removeWords, stopwords("english")) %>%
  tm_map(stripWhitespace)

wordcloud(words = wordCorpus,
          random.order = FALSE,
          col = "red")
```


